Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-21 prop_letter.tex
prop_letter.tex Follow "REVTEX 4.1 Author's Guide" to break down equations...
prop_letter.tex and prop_letter.lyx Sync...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\citep{Feynman1982Simulating}, Landauer~\citep{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. In order
to analyze the quantum world with finite resource, we extend the classical
interval-valued probability measure (IVPM)~\citep{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

@@

Although considering IVPM is new for quantum, people have already
defined classical IVPMs~\citep{JamisonLodwick2004}. We find if we
restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
quantum IVPMs are one-to-one corresponding to the classical ones.
Despite restricting on the domain of quantum IVPMs, if we pick the
range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
then quantum IVPMs becomes real-valued probability measures which
case Gleason's theorem applies. In the next paragraph, we will show
the Kochen-Specker theorem is another limit case when the collection
of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

@@

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that 
\begin{subequations}
\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\end{eqnarray}
\end{subequations}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that
there is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\citep{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
& & 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)

@@

& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
& & 1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
& & 1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
& & 1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{subequations}
\label{eq:non-Kernaghan}
\begin{eqnarray}
& & 1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
& & 1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
& & 1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
& & 1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
& & 1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
& & 1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
& & 1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
& & 1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
& & 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
\end{eqnarray}
\end{subequations}
\qed\end{example}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. In order
to analyze the quantum world with finite resource, we extend the classical
interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

@@

Although considering IVPM is new for quantum, people have already
defined classical IVPMs~\cite{JamisonLodwick2004}. We find if we
restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
quantum IVPMs are one-to-one corresponding to the classical ones.
Despite restricting on the domain of quantum IVPMs, if we pick the
range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
then quantum IVPMs becomes real-valued probability measures which
case Gleason's theorem applies. In the next paragraph, we will show
the Kochen-Specker theorem is another limit case when the collection
of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

@@

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that 
\begin{subequations}
\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
 &  & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\end{eqnarray}
\end{subequations}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that
there is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) \nonumber \\*
  &   & + f(0, 0, 0, 1) \textrm{ and} \\
1 & = & f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) \nonumber \\*
  &   & + f(1, 1, 1, -1)

@@

1 & = & f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) \nonumber \\*
  &   & + f(0, 0, 1, -1)\textrm{ ,}\\
1 & = & f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) \nonumber \\*
  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
1 & = & f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) \nonumber \\*
  &   & + f(0, 1, -1, 0)\textrm{ ,}\\
1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) \nonumber \\*
  &   & + f(0, 1, 0, -1)\textrm{ ,}\\
1 & = & f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) \nonumber \\*
  &   & + f(1, 0, 0, -1)\textrm{ ,}\\
1 & = & f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) \nonumber \\*
  &   & + f(1, -1, 0, 0)\textrm{ ,}\\
1 & = & f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) \nonumber \\*
  &   & + f(1, -1, -1, 1)\textrm{ ,}\\
1 & = & f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) \nonumber \\*
  &   & + f(1, 1, -1, -1)\textrm{ ,}\\
1 & = & f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) \nonumber \\*
  &   & + f(1, -1, -1, 1)\textrm{ .}

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{subequations}
\label{eq:non-Kernaghan}
\begin{eqnarray}
1 & = & f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1) \nonumber \\*
  &   & +f(1,0,0,1)\textrm{ ,}\\ 
1 & = & f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1) \nonumber \\*
  &   & +f(1,0,0,1)\textrm{ ,}\\ 
1 & = & f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,0,1,0)\textrm{ ,}\\ 
1 & = & f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,0,1,0)\textrm{ ,}\\ 
1 & = & f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1) \nonumber \\*
  &   & +f(1,1,-1,-1)\textrm{ ,}\\ 
1 & = & f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1) \nonumber \\*
  &   & +f(1,1,0,0)\textrm{ ,}\\ 
1 & = & f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
1 & = & f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1) \nonumber \\*
  &   & +f(1,1,1,-1)\textrm{ ,}\\ 
1 & = & f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0) \nonumber \\*
  &   & +f(1,1,1,1)\textrm{ ,}\\ 
1 & = & f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1) \nonumber \\*
  &   & +f(1,1,1,1)\textrm{ .} 
\end{eqnarray}
\end{subequations}
\qed\end{example}
